Digital Analysis of Paintings

### 2014-05-07 paper.tex
More changes :-)

% TODO technique.
The method for this technique is to decompose the image using wavelets. In this
paper quadrature mirror filters; filters which split an input signal into two
bands; are used to split the frequency space into multiple scales and
orientations. This produces a statistical model at each scale and orientation;
known as a subband.

@@

>>>>

The method for this technique is to decompose the image using wavelets. In this
paper quadrature mirror filters; filters which split an input signal into two
bands; are used to split the frequency space into multiple scales and
orientations. This produces a statistical model at each scale and orientation;
known as a subband.

@@

Using computer vision to segment brushstrokes is a difficult task; often
requiring expert knowledge of the painter and manual intervention to enable the
process. \cite{jia12rhythmic} shows a method for the automatic extraction of
brushstrokes.

This method involves a complex process; first the image has an edge detection
algorithm applied to it, then these edges are pruned to remove noisy, short and
unconnected edges to improve the actual segmentation of strokes.

Because an edge detector doesn't always pick up the full brushstroke, any gaps
in the painting are enclosed using a greedy process of scanning neighbours and
linking the nearest via a straight line if they are within a certain distance.

Any fully enclosed brushstrokes are then extracted and checked against an upper
and lower threshold for size. These thresholds were pre-selected to give a good
estimate for the size of a brushstroke. This is finally labelled a brushstroke
if the backbone is not too branched, it has a reasonable ratio of broadness to
length and the size of the stroke is proportional to the backbone of the
stroke.

After this process is complete, the image is then segmented with regard to
colour (\gls{RGB}) and directions (horizontal and vertical). $k$-means
clustering is then applied multiple times, gradually decreasing the threshold
for the average distance in the cluster. Any sufficiently small clusters are
removed at each step and are not considered in the future runs of the $k$-means
algorithm. This process is done to remove any noisy components there might be
in the digitisation of the image.

Brushstrokes which are already labelled are then removed and any remaining
clusters are labelled according to the same process.
